Ensuring Fairness with Transparent Auditing of Ethical Bias in AI Systems\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-04-24 abstract.tex
Added intro first two paragraph

\begin{IEEEkeywords}
keyword, keyword
\end{IEEEkeywords}

>>>>

\section{Introduction}
In recent years, the accelerating pace of artificial intelligence (AI) technologies have revolutionized numerous fields. In healthcare, AI-driven diagnostic systems streamline disease identification, while in finance, automated trading algorithms analyze market trends to execute optimal trades swiftly. This remarkable progress has reached diverse industries,sprouting out various applications for different purposes.

One of its most profound impact is how AI has transformed decision-making processes across sectors. By harnessing vast amounts of data and employing advanced algorithms, AI empowers organizations to make more informed and strategic decisions. From assessing job applicants to determining school admissions, AI-driven insights offer efficient and analytical advantages.

\section{Ease of Use}
bias sources example (COMPAS)
fairness is subjective, based on culture and often not quantitative
for AI system we use quantitative fairness measures
transparency and objectivity example : COMPAS
third party needed for auditing example : propublica like entity can use our stuff; we're not replacing but supplement; domain knowledge
we propose a framework
